Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-11 csf-2017/paper.tex
Start thinking about Related Work.

\begin{itemize}
\item Dreyer-Neis-Birkedal
\item CHERI papers
\item Akram's thesis
\item \url{http://2016.splashcon.org/event/splash-2016-oopsla-gentrification-gone-too-far-affordable-2nd-class-values-for-fun-and-co-effect}
\item other papers that enforce well-bracketed control flow at low level
(using a trusted stack manager)
\begin{itemize}
\item \url{http://ieeexplore.ieee.org/abstract/document/7536364/}
\item \url{http://ieeexplore.ieee.org/abstract/document/7536366/}
\item other stuff?
\end{itemize}
\end{itemize}

>>>>

Cap-mach:
\begin{itemize}
\item \cite{Watson2015Cheri} CHERI papers
\item \cite{akram_el-korashy_formal_2016}
\end{itemize}

Logical relation:
\begin{itemize}
\item \cite{Hur:2011:KLR:1926385.1926402}
\item \cite{Dreyer:jfp12}
\item \cite{Devriese:2016ObjCap}
\item \cite{osvald_gentrification_2016}
\end{itemize}

Other papers that enforce well-bracketed control flow at low level (using a
trusted stack manager)
\begin{itemize}
\item \cite{patrignani_modular_2016-1}
\item \cite{juglaret_beyond_2016-1}
\item other stuff?
\end{itemize}
